We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-02-19 paper/paper.tex
results previous publications

>>>>

\begin{table*}
\centering
\begin{tabular}{|p{2.5cm}|p{6cm}| p{5cm}| c|}\hline
Reference & Target Measurement & Parent Sample & Probability ($\%$)\\\hline
\text{\cite{2005A&A...431..517K}} & Disk height in MW's 11 classical
satellites & Monte Carlo satellite distributions with a power law
radial distribution. & $0.5$ \\
\hline
\end{tabular}
\caption{Probability results derived in previous publications.}
\end{table*}
